### 2019-03-15 1_introduction.tex
Add new section.

\section{Introduction}

@@

\begin{itemize}
\item Section~\ref{sec:metg} defines the METG metric.
\item Section~\ref{sec:task-bench} describe the design of Task Bench.
\item Section~\ref{sec:implementation} details the implementation of
  Task Bench in 13 runtime systems.
\item Section~\ref{sec:evaluation} provides a comprehensive evaluation
  of Task Bench performance on up to 64 nodes of the Cori
  supercomputer.
\end{itemize}

>>>>

\section{Introduction}
\label{sec:introduction}

@@

\begin{itemize}
\item Section~\ref{sec:metg} defines the METG metric and its
  relationship to quantities of interest to application developers.
\item Section~\ref{sec:task-bench} describes the design of Task Bench.
\item Section~\ref{sec:implementation} details the implementation of
  Task Bench in 13 runtime systems.
\item Section~\ref{sec:evaluation} provides a comprehensive evaluation
  of Task Bench performance on up to 64 nodes of the Cori
  supercomputer.
\end{itemize}
